White Dwarf Mergers on Adaptive Meshes\\ I. Methodology and Code Verification

### 2015-09-21 papers/wdmerger_I/paper.tex
Add description of the source-term predictor to the appendix.

\subsection{Gravity and Rotation Tracing}

@@

>>>>

\subsection{Gravity and Rotation Tracing}
\label{sec:gravity_rotation_tracing}

@@

\subsection{Source Term Predictor for the Hydrodynamics}

In the original release of \castro\ the value of the gravitational and rotation
source terms used in constructing the edge-states for the hydrodynamics update
was the time-level $n$ value. While this is formally second-order accurate, there
is a better choice one can make. We have information about the trend of these
source terms from previous timesteps, so we can use a predictor method to guess
at a more accurate value of the gravitational and rotational fields at the
$n+1/2$ time-level the hydro is evaluated at. Our method uses a lagged linear
extrapolation. Going into the hydro update, we have both the time-level $n$ and
time-level $n-1$ data for $g$ and $f_R$ (as defined in \autoref{sec:gravity_rotation_tracing}).
From this one can construct a simple linear estimator of (say) the gravitational
acceleration using a backward difference scheme at time-level $n$:
\begin{equation}
  \mathbf{g}(t_n + \Delta t) = \mathbf{g}(t_n) + \Delta t \left.\frac{d\mathbf{g}}{dt}\right|_{n} = \frac{3}{2}\mathbf{g}(t_n) - \frac{1}{2}\mathbf{g}(t_{n-1}).
\end{equation}
Here we have assumed a constant timestep for simplicity, and constructed the time derivative as
$d\mathbf{g} / dt = (\mathbf{g}(t_n) - \mathbf{g}(t_{n-1})) / \Delta t$. We perform this
predictor for the rotation field as well. While both this method and the original
method have second-order convergence properties, we have seen from testing that
this new method is slightly more accurate in absolute terms.
